|

### 2024-09-04 manuscript/paperCMSACversion.Rmd

As mentioned earlier, the outcome of this study is relevant to the debates about regulations and discourse around head trauma in hockey. An accurate analysis is imperative to prevent the spread of misinformed conclusions. ... talk about our conclusions

@@

 \hline
\end{tabular}
\end{center}
\caption{Comparing enforcers to non enforcers when enforcer is defined as E-F \label{tab:EDAEF}}
\end{table}

@@

\caption{Comparing enforcers to non enforcers when enforcer is defined as E-P \label{tab:EDAEP}}
\end{table}

>>>>

As mentioned earlier, the outcome of this study is relevant to the debates about regulations and discourse around head trauma in hockey. An accurate analysis is imperative to prevent the spread of misinformed conclusions and best inform regulatory safety practices going forward.

... talk about our conclusions

@@

 \hline
\end{tabular}
\end{center}
\caption{Comparing enforcers to non-enforcers when enforcer is defined as E-F \label{tab:EDAEF}}
\end{table}

@@

\caption{Comparing enforcers to non-enforcers when enforcer is defined as E-P \label{tab:EDAEP}}
\end{table}
